---
title: "Introduction to Data Science - HW 3"
author: "Shyla Alessandro- `salessandro4217@floridapoly.edu`"
output:
  html_document:
    df_print: paged
---



# Problem 1 

Create the following vectors in `R` (see the pattern and use appropriate functions to construct these vectors):

$a = (5, 10, 15, 20, ..., 160)$
```{r}

#a
vector_1 <- seq(5, 160, 5)
print(vector_1)

```

$b = (87, 86, 85, ..., 56)$

```{r}

#b
vector_2 <- seq(87, 56, -1)
print(vector_2)

```

(a) (5 points) Multiply these vectors and call the result `d`. 

```{r}

#a
d = vector_1 * vector_2
print(d)

```
(b) (5 points) What are the 19th, 20th, and 21st elements of `d`?

```{r}

#b
d[19]
d[20]
d[21]

```

(c) (5 points) What are all of the elements of `d` which are less than 2000?

```{r}

#c

less_than = d < 2000
print(less_than)


```

(d) (5 points) How many elements of `d` are greater than 6000?

```{r}
elements = d > 6000
print(elements)
```
# Problem 2

Start with this vector of `nouns`.  

```{r}
nouns <- c("apple", "flower", "insect", "lettuce", "knife", "dog", "cloud", "person", "cabinet", "flower" )
```

(a) (5 points) Use the `length()` function to display the number of elements in `nouns`.


```{r}

#a
nouns <- c("apple", "flower", "insect", "lettuce", "knife", "dog", "cloud", "person", "cabinet", "flower" )
length(nouns)

```

(b) (5 points) Use indexing to create a new vector consisting of the first 4 elements of `nouns`.

```{r}

#b
nouns <- c("apple", "flower", "insect", "lettuce", "knife", "dog", "cloud", "person", "cabinet", "flower" )
first_elements <- nouns[1:4]
print(first_elements)

```

(c) (5 points) Use indexing to create a new vector consisting of only the last 8 elements of `nouns`.

```{r}

nouns <- c("apple", "flower", "insect", "lettuce", "knife", "dog", "cloud", "person", "cabinet", "flower" )
last_elements <- nouns[3:10]
print(last_elements)

```
(d) (5 points) Use indexing to create a new vector of the 1st, 3rd through 6th, and 10th elements of `nouns` (the length of the resulting vector should be 6)

```{r}

nouns <- c("apple", "flower", "insect", "lettuce", "knife", "dog", "cloud", "person", "cabinet", "flower" )
component_1 <- nouns[1]
component_2 <- nouns[3:6]
component_3 <- nouns[10]
random_selection <- c(component_1, component_2, component_3)
print(random_selection)

```
# Problem 3

(a) (5 points) Create a vector `my_breakfast` of everything you ate for breakfast

```{r}

my_breakfast <- c("tater_tots","biscuit_and_gravy", "turkey_bacon", "lemonade" )
print(my_breakfast)

```
(b) (5 points) Create a vector `my_lunch` of everything you ate (or will eat) for lunch

```{r}

my_lunch <- c("veggies", "chicken", "lentils" )
print(my_lunch)

```
(c) (5 points) Create a list `meals` that has contains your breakfast and lunch

```{r}

my_breakfast <- c("tater_tots","biscuit_and_gravy", "turkey_bacon", "lemonade" )
my_lunch <- c("veggies", "chicken", "lentils" )
meals <- list(
  my_breakfast,
  my_lunch
  )
print(meals)
```
(d) (5 points) Add a "dinner" element to your `meals` list that has what you plan to eat for dinner

```{r}

my_breakfast <- c("tater_tots","biscuit_and_gravy", "turkey_bacon", "lemonade" )
my_lunch <- c("veggies", "chicken", "lentils" )
my_dinner <- c("protein_shake", "egg_whites" )
meals <- list(
  my_breakfast,
  my_lunch,
  my_dinner
  )
print(meals)

```

(e) (5 points) Use dollar notation to extract your `dinner` element from your list and save it in a vector called 'dinner'

```{r}

my_breakfast <- c("tater_tots","biscuit_and_gravy", "turkey_bacon", "lemonade" )
my_lunch <- c("veggies", "chicken", "lentils" )
my_dinner <- c("protein_shake", "egg_whites" )
meals <- list(
  my_breakfast,
  my_lunch,
  my_dinner
  )

meals$my_dinner
print(dinner)

```


(f) (5 points) Use double-bracket notation to extract your `lunch` element from your list and save it in your list as the element at index 5 (no reason beyond practice)

```{r}

my_breakfast <- c("tater_tots","biscuit_and_gravy", "turkey_bacon", "lemonade" )
my_lunch <- c("veggies", "chicken", "lentils" )
my_dinner <- c("protein_shake", "egg_whites" )
meals <- list(
  my_breakfast,
  my_lunch,
  my_dinner
  )

meals[[5]] <- meals[[2]]
print(meals[[5]])

```

# Problem 4

(a) (5 points) Create a vector of the number of points the Chicago Bulls (NBA team) scored in the most recent 4 games of the season (Google "Chicago Bulls" for the scores!)

```{r}

points_scored <- c(100, 95, 81, 114 )
print(points_scored)

```

(b) (5 points) Create a vector of the number of points the Bulls have allowed to be scored against them in each of the first 4 games of the season

```{r}

l_count <- c(116, 119, 111, 110 )
print(l_count)
```

(c) (5 points) Combine your two vectors into a dataframe called `games`

```{r}

points_scored <- c(100, 95, 81, 114 )
l_count <- c(116, 119, 111, 110 )
games <- data.frame(points_scored, l_count)
print(games)

```

(d) (5 points) Create a new column "diff" that is the difference in points between the teams. Hint: recall the syntax for assigning new elements (which in this case will be a vector) to a list!

```{r}

points_scored <- c(100, 95, 81, 114 )
l_count <- c(116, 119, 111, 110 )
diff <- abs(l_count - points_scored)
games <- list(
  points_scored,
  l_count,
  diff
)

new_chart <- data.frame(points_scored, l_count, diff )
print(new_chart)

```

(e) (5 points) Create a new column "won" which is `TRUE` if the Bulls won the game.

```{r}

points_scored <- c(100, 95, 81, 114 )
l_count <- c(116, 119, 111, 110 )
diff <- abs(l_count - points_scored)
won <- points_scored > l_count
games <- list(
  points_scored,
  l_count,
  diff,
  won
)

new_chart <- data.frame(points_scored, l_count, diff, won )
print(new_chart)

```

(f) (5 points) Create a vector of the opponent names corresponding to the games played and add it to your dataframe.

```{r}

points_scored <- c(100, 95, 81, 114 )
l_count <- c(116, 119, 111, 110 )
diff <- abs(l_count - points_scored)
won <- points_scored > l_count
opponent <- 'Bucks'
games <- list(
  points_scored,
  l_count,
  diff,
  won,
  opponent
)

new_chart <- data.frame(points_scored, l_count, diff, won, opponent )
print(new_chart)
  
```

